Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-04 mu/article/article.tex
sab

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is hold
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the 2D and bulk structures.
% 
\begin{table}[t]
\begin{tabular}{cccccc}
\hline
\hline
Kind of  & 
\multirow{2}{*}{\quad Structure \quad} & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
system & & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\hline
2D   & \emph{up}    & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
     &              &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
     &              &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
\hline
2D   & \emph{alt}   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
     &              &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
\hline
bulk &  CdSe        & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
\hline
bulk &  GaAs        & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\hline
\end{tabular}
\caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
for different structures and the corresponding polarization angles and energy
values.}
\label{tab:vab-str-comp}
\end{table}

>>>>

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is hold
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the 2D and bulk structures.
% 
\begin{table}[t]
\begin{tabular}{cccccc}
\hline
\hline
Kind of  & 
\multirow{2}{*}{\quad Structure \quad} & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
system & & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\hline
2D   & \emph{up}    & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
     &              &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
     &              &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
\hline
2D   & \emph{alt}   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
     &              &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
\hline
bulk &  CdSe        & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
\hline
bulk &  GaAs        & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\hline
\end{tabular}
\caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
for different structures and the corresponding polarization angle $\alpha$ and energy
values.}
\label{tab:vab-str-comp}
\end{table}
